Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-10 examples.tex
+

@@

\begin{figure}
\begin{lstlisting}
;; Assume the save-space is in rdi,
;; load-space in rsi
;; No need to save/restore caller-save regs
;; Save yielding context
$\specline{}$  
mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15
mov 56[%rdi], %cr3
;; Restore target context
mov %rbx, 0[%rsi] 
;; This switches to a new stack
;; This stack may not be mapped in the
;; current address space!
mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]
;; Switch to the new address space
mov %cr3, 56[%rsi]
\end{lstlisting}
\caption{Basic task switch code that switches address spaces.}
\label{fig:swtch}
\end{figure}

>>>>

  \todo[inline,color=yellow]{Colin, could you speak about the fact that we have wpd in iProp so that's the reason to have rtval whereever table traversal is needed}

@@

;; Assume the save-space is in rdi,
;; load-space in rsi
;; No need to save/restore caller-save regs
;; Save yielding context
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)}$
$\specline{ \texttt{rsi}\mapsto_{r} \rtv' \ast \texttt{rdi}\mapsto_{r} \_ \ast \texttt{rbx}\mapsto_{r} \texttt{rbxv} \ast  \texttt{rsp}\mapsto_{r} \texttt{rspv} \ast \texttt{rbp}\mapsto_{r} \texttt{rbpv} }$
$\specline{\texttt{r12}\mapsto_{r} \texttt{r12v} \ast \texttt{r13}\mapsto_{r} \texttt{r13v} \ast \texttt{r14}\mapsto_{r} \texttt{r14v} \ast \texttt{r15}\mapsto_{r} \texttt{r15v}}$
$\specline{\texttt{rdi+0} \mapsto_{v,\rtv} \_ \ast \texttt{rdi+8} \mapsto_{v,\rtv} \_ \ast \texttt{rdi+16} \mapsto_{v,\rtv} \_ \ast \texttt{rdi+24} \mapsto_{v,\rtv} \_ \ast \texttt{rdi+32} \mapsto_{v,\rtv} \_}$
$\specline{\texttt{rdi+40} \mapsto_{v,\rtv} \_ \ast \texttt{rdi+48} \mapsto_{v,\rtv} \_\ast \texttt{rdi+56} \mapsto_{v,\rtv} \_}$
mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)}$
$\specline{ \texttt{rdi}\mapsto_{r} \_ \ast \texttt{rbx}\mapsto_{r} \texttt{rbxv} \ast  \texttt{rsp}\mapsto_{r} \texttt{rspv} \ast \texttt{rbp}\mapsto_{r} \texttt{rbpv} }$
$\specline{\texttt{r12}\mapsto_{r} \texttt{r12v} \ast \texttt{r13}\mapsto_{r} \texttt{r13v} \ast \texttt{r14}\mapsto_{r} \texttt{r14v} \ast \texttt{r15}\mapsto_{r} \texttt{r15v}}$
$\specline{\texttt{rdi+0} \mapsto_{v,\rtv} \texttt{rbxv} \ast \texttt{rdi+8} \mapsto_{v,\rtv} \texttt{rspv} \ast \texttt{rdi+16} \mapsto_{v,\rtv} \texttt{rbpv} \ast \texttt{rdi+24} \mapsto_{v,\rtv} \texttt{r12v} \ast \texttt{rdi+32} \mapsto_{v,\rtv} \texttt{r13v}}$
$\specline{\texttt{rdi+40} \mapsto_{v,\rtv} \texttt{r14v} \ast \texttt{rdi+48} \mapsto_{v,\rtv} \texttt{r15v}\ast \texttt{rdi+56} \mapsto_{v,\rtv} \_}$
mov 56[%rdi], %cr3
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)}$
$\specline{ \texttt{rdi}\mapsto_{r} \_ \ast \texttt{rbx}\mapsto_{r} \texttt{rbxv} \ast  \texttt{rsp}\mapsto_{r} \texttt{rspv} \ast \texttt{rbp}\mapsto_{r} \texttt{rbpv} }$
$\specline{\texttt{r12}\mapsto_{r} \texttt{r12v} \ast \texttt{r13}\mapsto_{r} \texttt{r13v} \ast \texttt{r14}\mapsto_{r} \texttt{r14v} \ast \texttt{r15}\mapsto_{r} \texttt{r15v}}$
$\specline{\texttt{rdi+0} \mapsto_{v,\rtv} \texttt{rbxv} \ast \texttt{rdi+8} \mapsto_{v,\rtv} \texttt{rspv} \ast \texttt{rdi+16} \mapsto_{v,\rtv} \texttt{rbpv} \ast \texttt{rdi+24} \mapsto_{v,\rtv} \texttt{r12v} \ast \texttt{rdi+32} \mapsto_{v,\rtv} \texttt{r13v}}$
$\specline{\texttt{rdi+40} \mapsto_{v,\rtv} \texttt{r14v} \ast \texttt{rdi+48} \mapsto_{v,\rtv} \texttt{r15v}\ast \texttt{rdi+56} \mapsto_{v,\rtv} \rtv}$    
;; Restore target context
mov %rbx, 0[%rsi] 
;; This switches to a new stack
;; This stack may not be mapped in the
;; current address space!
mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,\gammaPred,\rtv)}$
$\specline{ \texttt{rdi}\mapsto_{r} \_ \ast \texttt{rbx}\mapsto_{r} \texttt{rbxv} \ast  \texttt{rsp}\mapsto_{r} \texttt{rspv} \ast \texttt{rbp}\mapsto_{r} \texttt{rbpv} }$
$\specline{\texttt{r12}\mapsto_{r} \texttt{r12v} \ast \texttt{r13}\mapsto_{r} \texttt{r13v} \ast \texttt{r14}\mapsto_{r} \texttt{r14v} \ast \texttt{r15}\mapsto_{r} \texttt{r15v}}$
$\specline{\texttt{rdi+0} \mapsto_{v,\rtv} \texttt{rbxv} \ast \texttt{rdi+8} \mapsto_{v,\rtv} \texttt{rspv} \ast \texttt{rdi+16} \mapsto_{v,\rtv} \texttt{rbpv} \ast \texttt{rdi+24} \mapsto_{v,\rtv} \texttt{r12v} \ast \texttt{rdi+32} \mapsto_{v,\rtv} \texttt{r13v}}$
$\specline{\texttt{rdi+40} \mapsto_{v,\rtv} \texttt{r14v} \ast \texttt{rdi+48} \mapsto_{v,\rtv} \texttt{r15v}\ast \texttt{rdi+56} \mapsto_{v,\rtv} \rtv}$    
;; Switch to the new address space
mov %cr3, 56[%rsi]
\caption{Basic task switch code that switches address spaces.}
\label{fig:swtch}
